Summary Tables

### 2020-02-28 summary_tables.Rmd
Add true distances per person as well

>>>>

## Distance tables by using true distance
Case study specific distance tables for baseline and five scenarios

for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$true_dist %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)

  count_people <- length(unique(io[[city]]$trip_scen_sets$participant_id))
  td <- io[[city]]$true_dist %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL
